Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_3-microservice.tex
syntax

The API convention of \emph{/<MODULE>/<DATA_FORMAT>/<DATA_OPERATION_TYPE>} allows users to integrate new import or export modules into the system as well as add new data types.

>>>>

The API convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_OPERATION\_TYPE} allows users to integrate new import or export modules into the system as well as add new data types.
